---
title: "Test_Functionality"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test_Functionality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This test markdown covers and example workflow of a user of the package. 
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Bring in the new package
```{r setup}
library(DBconEZ)
```

Check all available ODBC drivers
```{r}
sort(unique(odbcListDrivers()[[1]])) 
```




Next establish a connection to a DB. In this example we are checking a MySQL db, for the purposes of this exercise only. IP address is internal, password and user are self-expiring after one login.
```{r}
con <- DBconnect(RMySQL::MySQL(), 
                 dbname = "sakila", 
                 host = "192.168.50.71", 
                 port = 49153,
                 user = "root",
                 password = "Camplovers01")

```


Next we can use the dm_from_src function to creat a DM (data model) of the available schemas/tables. The example connection connects to only a single schema 
```{r}
con_dm <- dm_from_src(con, learn_keys = FALSE) 
```

We can then see if an ERD diagram can be drawn from available information of the Database *This is an experimental function in the dm package and as such is quite buggy itself)

```{r}
dm_draw(con_dm)

```

We can then test a query of the database using an analytical type of request from a stakeholder
##You want to run an email marketing campaign in Canada, for which you will need the names and email addresses of all Canadian customers. 

```{r}
email_results <- dbGetQuery(con, "select concat(c.first_name,' ',c.last_name) as 'Name', c.email as 'E-mail'
	from customer as c
	join address as a on c.address_id = a.address_id
	join city as cy on a.city_id = cy.city_id
	join country as ct on ct.country_id = cy.country_id
	where ct.country = 'Canada';")

```

```{r comment='', echo=FALSE, results='asis'}
 knitr::kable(email_results, caption = "Email Query", floating.environment="sidewaystable")
```


Let's try a more complicated query
##List the top five genres in gross revenue in descending order
```{r}
sales_dollars_genre <- dbGetQuery(con, "select c.name as 'Film', sum(p.amount) as 'Gross Revenue'
	from category as c
	join film_category as fc on fc.category_id = c.category_id
	join inventory as i on i.film_id = fc.film_id
	join rental as r on r.inventory_id = i.inventory_id
	join payment as p on p.rental_id = r.rental_id
	group by c.name
	order by sum(p.amount) desc
	limit 5;
")


```

```{r comment='', echo=FALSE, results='asis'}
 knitr::kable(sales_dollars_genre, caption = "Sales by Genre", floating.environment="sidewaystable")
```
##We see here that the BDconEZ package aids greatly in streamlining the process to explore and query data in a single place.
Future versions will include integration of the gWidgets GUI interface to streamline selection and querying inline code.

